%-------------------------
% ATS-Compatible LaTeX Resume
% Author: Jonathan Le
%-------------------------

\documentclass[11pt, onesided, letterpaper]{article}

% Packages
\usepackage[utf8]{inputenc}             % Character encoding
\usepackage[T1]{fontenc}                % Font encoding
\usepackage[margin=1cm]{geometry}       % Page margins
\usepackage{enumitem}                   % List formatting
\usepackage{titlesec}                   % Title sections
\usepackage{hyperref}                   % Links
\usepackage{parskip}                    % Paragraph spacing

% Hyperlink setup (invisible for ATS, visible for humans)
\hypersetup{
    colorlinks=true,
    urlcolor=black,
    linkcolor=black,
    pdftitle={Jonathan Le - Resume},
    pdfauthor={Jonathan Le}
}

% Section formatting — bold, all caps, with horizontal rule
\titleformat{\section}
  {\bfseries\uppercase}     % Bold and uppercase titles
  {}                        % Empty label
  {0em}                     % Separator
  {}                        % Code before title
  [\titlerule]              % Code after title - horizontal line
\titlespacing{\section}{0pt}{2pt}{2pt}

% No page numbers
\pagestyle{empty}

% Tight list spacing
\setlist[itemize]{leftmargin=1.5em, itemsep=1pt, topsep=2pt, parsep=0pt}

\begin{document}

%-------------------------
% HEADER
%-------------------------
\begin{center}
    {\LARGE \textbf{Jonathan Le}} \\[4pt]
    jonathanlemain@gmail.com |
    780-655-6719 |
    \href{https://github.com/Jonathan-C-L}{github.com/Jonathan-C-L} |
    \href{https://jonathan-c-l.github.io/portfolio-page}{jonathan-c-l.github.io/portfolio-page}
\end{center}

%-------------------------
% TECHNICAL SKILLS
%-------------------------
\section{Technical Skills}

\textbf{Languages:} C\#, Python, TypeScript, JavaScript, PHP, C, SQL \\
\textbf{Frameworks:} Node.js, Express.js, React, C\#.NET (8.0), ASP.NET ADO, Entity Framework, jQuery, LINQ, Raylib, Webpack \\
\textbf{Databases:} MySQL, Microsoft SQL Server \\
\textbf{Tools:} Git, GitHub, Microsoft Azure, VS Code, Unity, Power BI, CPanel, uv \\
\textbf{Practices:} REST APIs, Object-Oriented Programming, Full-Stack Development, CRUD Operations, Agile, Scrum, Kanban, Jira, Embedded Systems, Optimizations

%-------------------------
% PROJECTS
%-------------------------
\section{Projects}

\textbf{Personal Portfolio Website} | \textit{JavaScript, HTML, CSS --- Individual}  \hfill Ongoing
\begin{itemize}
    \item Designed and deployed a full-stack personal portfolio website hosted on GitHub Pages, demonstrating end-to-end web development skills including design, development, and deployment.
    \item Integrated GitHub public REST API calls for automatic pulling of project and resume information.
\end{itemize}

\vspace{4pt}
\textbf{Cartesian to G-Code Translation Application} | \textit{C, C\# --- Group} \hfill Jan 2026 -- Apr 2026

\begin{itemize}
    \item Engineered a C\# desktop application that receives real-time position data from a microcontroller and visualizes motion output with a hardware-to-display latency under 10 ms.
    \item Developed a scalable 3D visualizer in C using Raylib, replicating x/y/z positional changes with precision to 6 significant decimal digits.
    \item Led a 2-person development team using Git version control and Agile sprint planning, coordinating deliverables with multiple external stakeholders.
\end{itemize}

\vspace{4pt}
\textbf{Just Juniors} | \textit{C\#, Unity --- Group (Video Game Competition)} \hfill Present

\begin{itemize}
    \item Designed and implemented a persistent inventory management system in C\# tracking player-discovered items across game sessions.
    \item Refactored game loop logic to decouple inventory state from player progression, reducing complexity and improving runtime efficiency.
    \item Collaborated and communicated with a 12 person team, using Git version control and Agile sprint planning, to consistently present deliverables with stakeholders.
\end{itemize}

%-------------------------
% WORK EXPERIENCE
%-------------------------
\section{Work Experience}

\textbf{IT Support / Receptionist} | \textit{Glenora Family Dental} \hfill Jun 2021 -- Jun 2022

\begin{itemize}
    \item Provided Tier 1 IT support to staff: installed, configured, and troubleshot workstations, printers, and software packages, minimizing downtime.
    \item Served as the primary point of contact for all inbound communication (email, phone, in-house messaging), demonstrating strong customer service and communication skills.
    \item Coordinated IT-related communication between management and production staff, escalating unresolved issues appropriately.
\end{itemize}

%-------------------------
% EDUCATION
%-------------------------
\section{Education}

\textbf{Computer Engineering Tech Diploma} | \textit{Northern Alberta Institute of Technology}  \hfill Sept 2024 -- Apr 2026

\begin{itemize}
    \item Relevant coursework: Algorithms and Data Structures, Object-Oriented Design, Full-Stack Development, Database Systems and REST APIs, Embedded Systems.
\end{itemize}

\vspace{4pt}
\textbf{Bachelor of Science, Honours with Distinction} | \textit{University of Alberta}  \hfill Aug 2019 -- Jun 2022

\begin{itemize}
    \item Awarded Honours with Distinction --- conferred on fewer than 5\% of graduating students.
\end{itemize}

%-------------------------
% LEADERSHIP AND MENTORSHIP
%-------------------------
\section{Leadership and Mentorship}

\textbf{STEM Mentor} | \textit{Skillcity Institute} \hfill May 2025 -- Present

\begin{itemize}
    \item Mentor youth aged 8 to 17 in web development, electronics, and robotics; design hands-on curricula making complex technical concepts accessible across skill levels.
\end{itemize}

\vspace{4pt}
\textbf{Volleyball Coach} | \textit{Adult Recreation Program} \hfill Jul 2023 -- Present

\begin{itemize}
    \item Lead instructional sessions for groups of up to 20 adult beginners, developing lesson plans, delivering technique coaching, and fostering a collaborative learning environment.
\end{itemize}

\end{document}